A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-06-27 multiple.tex
WOW IT FITS

\begin{figure}
  \centering
\begin{prooftree}
  {% % LEFT TREE: here x_12 is zero
  \hypo{PROOF CLOSED}
  \infer1[\Propagate]{WHAT HAPPENS WHEN X_12 IS ZERO}
  }% END LEFT TREE
  {% RIGHT TREE % here x_12 is one
  \hypo{r} 
  }% END RIGHT TREE
  \infer2[\Split{} $\TransitionVar_{12} = 0$]{
  \begin{aligned}
    \TransitionVar_7 = l_A - \TransitionVar_9 - 2\TransitionVar_{11}-2\TransitionVar_{12}\\
    \land \TransitionVar_2 = l_A - 3\\
    \land \TransitionVar_{8} = \TransitionVar_{11} + \TransitionVar_{12} - 1\\
    \land \TransitionVar_6 = \TransitionVar_{11}\\
    \land \TransitionVar_{10} = 1 - \TransitionVar_{11}\\
    \land \Connected(B, \Filter) \\
    \land \Image{}_{\Tuple{A',B}, \Map}(\Filter, \VectorLiteral{l_A, 1, 2, l_A}) 
  \end{aligned}
  }
  \infer1[Expand $\sum$, \EquationReasoning] {
    \begin{aligned}
      l_A = \sum_{k = 6}^{k = 12} \TransitionVar_k\\
      \land \TransitionVar_2 = l_A - 3\\
      \land 1 + \TransitionVar_{8}   = \TransitionVar_{11} + \TransitionVar_{12}\\
      \land \TransitionVar_{11} = \TransitionVar_6\\
      \land \TransitionVar_{12} = \TransitionVar_8 + \TransitionVar_{10}\\
      \land \Connected(B, \Filter) \\
      \land \Image{}_{\Tuple{A',B}, \Map}(\Filter, \VectorLiteral{l_A, 1, 2, l_A}) 
    \end{aligned}
  }
  \infer1[\EquationReasoning: expand $\FlowEq$]{
    \begin{aligned}
      l_A = \sum_{k = 6}^{k = 12} \TransitionVar_k\\
      \land \TransitionVar_2 = l_A - 3\\
      \land \FlowEq(B, \Filter) \\
      \land \Connected(B, \Filter) \\
      \land \Image{}_{\Tuple{A',B}, \Map}(\Filter, \VectorLiteral{l_A, 1, 2, l_A}) 
    \end{aligned}
  }
  \infer1[Repeat \cref{fig:derivation:single}, $l_A = l_B$.]{
    \begin{aligned}
      l_B = \sum_{k = 6}^{k = 12} \TransitionVar_k\\
      \land i = \TransitionVar_5\\
      \land l_A = \sum_{k = 1}^{k = 5} \TransitionVar_k\\
      \land n = \TransitionVar_4 + \TransitionVar_1\\  
      \land \FlowEq(B, \Filter) \\
      \land \Connected(A', \Filter) \\
      \land \Connected(B, \Filter) \\
      \land \Image{}_{\Tuple{A',B}, \Map}(\Filter, \VectorLiteral{l_A, i, n, l_B}) 
      \land l_A = l_B\\
      \land l_A - i - n > 0\\
      \land 0 < i < n
    \end{aligned}
  }
  \infer1[\ExpandM]{
    \Image{}_{\Tuple{A', B}, \Map}(\Filter, \VectorLiteral{l_A, i, n, l_B})
    \land l_A = l_B % Implied constraint
    \land l_A - i - n > 0
    \land 0 < i < n
    }
\end{prooftree}
\caption{A derivation for \Calculus{} on the Parikh image strings for the
constraints of \cref{ex:string-constraints}. Note the constant propagation
for~$n$!}\label{fig:derivation:multi}
\end{figure}

>>>>

\begin{figure}
  \centering
\begin{prooftree}
  {% % LEFT TREE: here x_12 is zero
  \hypo{
      \ldots \land 1 = 0 
      \land \Image{}_{\emptyset, \Map}(\Filter, \VectorLiteral{l_A, 1, 2, l_A})
  }
  \infer1[\Materialise: $\emptyset$]{
    \begin{array}{llll}
      \TransitionVar_9 = 0 
      \land \TransitionVar_7 = l_A - 2 \\
      \land \TransitionVar_2 = l_A - 3
      \land \TransitionVar_{8} = 0 \\
      \land \TransitionVar_6 = \TransitionVar_{11} = 1
      \land \TransitionVar_{10} = 0 \\
      \land \Connected(B, \Filter)\\
      \land \Image{}_{\Tuple{A',B}, \Map}(\Filter, \VectorLiteral{l_A, 1, 2, l_A})
    \end{array}
  }
  \infer1[\Propagate{}]{
    \begin{array}{llll}
      \TransitionVar_{12} = 0 
      \land \TransitionVar_7 = l_A - \TransitionVar_9 - 2 \\
      \land \TransitionVar_2 = l_A - 3 
      \land \TransitionVar_{8} = 0 \\
      \land \TransitionVar_6 = \TransitionVar_{11} = 1 \\
      \land \TransitionVar_{10} = 0 
      \land \Connected(B, \Filter) \\
      \land \Image{}_{\Tuple{A',B}, \Map}(\Filter, \VectorLiteral{l_A, 1, 2, l_A}) 
    \end{array}
    }
  }% END LEFT TREE
  {% RIGHT TREE % here x_12 is > 0
  \hypo{
      \ldots \land 1 = 0 
      \land \Image{}_{\emptyset, \Map}(\Filter, \VectorLiteral{l_A, 1, 2, l_A})
  }
  \infer1[\Materialise: $\emptyset$]{
    \begin{array}{rrrr}
      \TransitionVar_{12} > 0 \land \\
      \TransitionVar_7 = l_A - \TransitionVar_9 - 2\TransitionVar_{11}-2\TransitionVar_{12} \land \\
      \TransitionVar_2 = l_A - 3 \land \\
      \TransitionVar_{8} = \TransitionVar_{11} + \TransitionVar_{12} - 1 \land \\
      \TransitionVar_6 = \TransitionVar_{11} \land\\
      \TransitionVar_{10} = 1 - \TransitionVar_{11} \land\\
      \Connected(B, \Filter) \land\\
      \Image{}_{\Tuple{A',B}, \Map}(\Filter, \VectorLiteral{l_A, 1, 2, l_A}) 
    \end{array}
  }
  }% END RIGHT TREE
  \infer2[\Split{} $\TransitionVar_{12} = 0$]{
  \begin{array}{llll}
    \TransitionVar_7 = l_A - \TransitionVar_9 - 2\TransitionVar_{11}-2\TransitionVar_{12} \\
    \land \TransitionVar_2 = l_A - 3 \\
    \land \TransitionVar_{8} = \TransitionVar_{11} + \TransitionVar_{12} - 1 \\
    \land \TransitionVar_6 = \TransitionVar_{11} \\
    \land \TransitionVar_{10} = 1 - \TransitionVar_{11} \\
    \land \Connected(B, \Filter)\\
    \land \Image{}_{\Tuple{A',B}, \Map}(\Filter, \VectorLiteral{l_A, 1, 2, l_A}) 
  \end{array}
  }
  \infer1[Expand $\sum$, \EquationReasoning] {
    \begin{array}{llll}
      l_A = \sum_{k = 6}^{k = 12} \TransitionVar_k
      \land \TransitionVar_2 = l_A - 3
      \land 1 + \TransitionVar_{8}   = \TransitionVar_{11} + \TransitionVar_{12}
      \land \TransitionVar_{11} = \TransitionVar_6 \\
      \land \TransitionVar_{12} = \TransitionVar_8 + \TransitionVar_{10}
      \land \Connected(B, \Filter) 
      \land \Image{}_{\Tuple{A',B}, \Map}(\Filter, \VectorLiteral{l_A, 1, 2, l_A}) 
    \end{array}
  }
  \infer1[\EquationReasoning: expand $\FlowEq$]{
    \begin{array}{llll}
      l_A = \sum_{k = 6}^{k = 12} \TransitionVar_k
      \land \TransitionVar_2 = l_A - 3
      \land \FlowEq(B, \Filter) \\
      \land \Connected(B, \Filter) 
      \land \Image{}_{\Tuple{A',B}, \Map}(\Filter, \VectorLiteral{l_A, 1, 2, l_A}) 
    \end{array}
  }
  \infer1[Repeat \cref{fig:derivation:single}, $l_A = l_B$.]{
    \begin{array}{llll}
      l_B = \sum_{k = 6}^{k = 12} \TransitionVar_k
      \land i = \TransitionVar_5
      \land l_A = \sum_{k = 1}^{k = 5} \TransitionVar_k \\
      \land n = \TransitionVar_4 + \TransitionVar_1
      \land \FlowEq(B, \Filter)
      \land \Connected(A', \Filter)\\
      \land \Connected(B, \Filter)
      \land \Image{}_{\Tuple{A',B}, \Map}(\Filter, \VectorLiteral{l_A, i, n, l_B}) \\
      \land l_A = l_B
      \land l_A - i - n > 0
      \land 0 < i < n
    \end{array}
  }
  \infer1[\ExpandM]{
    \Image{}_{\Tuple{A', B}, \Map}(\Filter, \VectorLiteral{l_A, i, n, l_B})
    \land l_A = l_B % Implied constraint
    \land l_A - i - n > 0
    \land 0 < i < n
    }
\end{prooftree}
\caption{A derivation for \Calculus{} on the Parikh image strings for the
constraints of \cref{ex:string-constraints}. Note the constant propagation
for~$n$!}\label{fig:derivation:multi}
\end{figure}
